\subsection{RSA Cryptosystem}
Cryptography is the study of secure communication between parties in an untrusted or unsecure communication channel.
Cryptography has three primary purposes for secure communications: provide confidentiality, authenticate entities, and verification of data.
Modern cryptography is based on hard math problems such as integer factorization, discrete logarithmic problem, and pre-image problems. 
Hard math problems are not found in $\P$ and found in $\NP$.
In most forms of modern cryptography, \textit{keys}, are data parameters used to form function outputs for the use in a communication channel.
There are three common types of keys in cryptography:
\begin{enumerate}
\item A \textit{secret key} is known by certain entities.  Typically a secret key is used by entities to encrypt and decrypt data that is communicated over an untrusted channel.  Secret keys require a secure channel to exchange between all entities.
\item When there are no means to exchange secret keys, one can use a private and public key scheme.
A \textit{public key} is a key that can be shared with any entity, i.e. trusted and untrusted entities can know it.
The \textit{private key} is a key that is kept to one entity. It is treated like a secret key and should only be known to that entity.
\end{enumerate}
A \textit{cryptosystem} is a suite of algorithms used to establish secure communication channel between parties. 
The RSA cryptosystem is the first practical cryptosystem in modern cryptography that allows for encryption of data (confidentiality), authentication of entites, and verify message integrity using just one underlying hard math problem, integer factorization.

RSA is named after its second inventors, Ron Rivest, Adi Shamir, and Leonard Adelmen.
These three individuals devised and published the algorithm in 1977.
The original inventor of RSA was Clifford Cocks in 1973 however, it was only known to the public since 1997 that Clifford Cocks was the original inventor because his was was classified by Government Communication Headquaters, an intelligence agency of the United Kingdom.

For the RSA cryptosystem, we first want to pose the communication security problem.  
Suppose we have two entities, Alice and Bob, that wish to communicate over an unsecure channel.
Should Alice and Bob agree to using RSA, each entity will have a pair of keys, a private key and a public key.
Most implementations of RSA use the following key derivation \cite{rivest1978method}:
\begin{enumerate}
\item Let $n=p\cdot q$ where $p$ and $q$ are randomly chosen prime numbers.
\item Choose an integer $e$ such that $1 < e \leq \phi (n)$ and $gcd\lr{e,\phi\lr{n}}=1$ where $\phi$ is the Euler totient function.
\item Let $d \equiv e^{-1} \mod \phi(n)$.
\end{enumerate}
The RSA cryptosystem is based around the following formula:
$$\left(m^e\right)^d \mod n= \left(m^d\right)^e \mod n\equiv m \mod n$$
where we have natural numbers $e$, $d$, $m$, and $n$, such that $m < n$ and $gcd(m,n)=1$.


%explain fermat's little theorem here
If Alice derives a public and private key in the manner described, her public key is $(n,e)$ and her private key is $d$.
Suppose Bob wants to send Alice a message $M$.  
Bob will represent $M$ in binary form, $m$.
%Suppose Bob wants to send Alice a natural number $m$ to Bob over an untrusted or insecure communication channel.  
%$m$ may represent a binary code of a message.
Alice sends her public key $(n,e)$ to Bob and keeps her private key $d$ secret.  
If $gcd(m,n)\neq 1$, then Bob modifies $m$ by padding $m$ with additional digits so that $m$ becomes co-prime with $n$.
There are efficient padding schemes to modify $m$ such that $m$ and $n$ are co-prime \cite{jonsson2003public}.
Bob sends the following value, $c$, to Alice:
$$c \equiv m^e \mod n$$
$c$ is said to be a ciphertext.
Alice can decrypt the ciphertext and recover $m$ by computing:
$$ m \equiv c^d \mod n = \lr{m^e}^d \mod n$$

The RSA cryptosystem is based on integer factorization and the RSA problem, given $n$ where $n=p\cdot q$ where $p$ and $q$ are prime numbers, find $p$ and $q$.
For sufficiently large integers, factorization and the RSA problem becomes very difficult.  
If there were an algorithm that solved integer factorization in polynomial time, then one can also solve the RSA problem as well.
Suppose a third party listens into the conversation and knows Alice's public key $(n,e)$ and the ciphertext $c$.
If the the third party can factor $n = p\cdot q$ then the attacker can computer $\phi(n)$ and compute $d \equiv e^{-1} \mod \phi(n)$ using the extended euclidian algorithm.
Once they have $d$, the attacker can compute $m \equiv c^d \mod n$.

Currently, the most efficient factorization algorithm is the general number sieve algorithm \cite{lenstra1993number}.
It's an exponential running time algorithm.
If a polynomial running time algorithm for integer factorization existed, it would allow for compromise of security that is provided to communicating parties by the RSA cryptosystem.
It would allow for a reduction of the integer factorization problem, a problem that exists in $\NP$ but not $\P$.
The algorithm would allow for an adversary to attack RSA \cite{menezes1996handbook} in polynomial time.



